### 2018-08-06 Sections/optical_encoding_of_quantum_information.tex
minor

\begin{figure}[htpb]
	\includegraphics[width=0.475\textwidth]{hermite_basis}
	\caption{The family of Hermite functions, $H_n(x)$, are an example of an orthonormal basis of continuous functions that could be utilised in the spatio-temporal encoding of qudits into photonic wave-packets. Shown here are \mbox{$n=0,1,2,3$}.}\index{Hermite functions}\label{fig:hermite_basis}
\end{figure}

>>>>

\begin{figure}[htpb]
	\includegraphics[width=0.475\textwidth]{hermite_basis}
	\caption{The family of Hermite functions, $H_n(x)$, modulated by Gaussian envelopes, are an example of an orthonormal basis of continuous functions that could be utilised in the spatio-temporal encoding of qudits into photonic wave-packets. Shown here are \mbox{$n=0,1,2,3$}.}\index{Hermite functions}\label{fig:hermite_basis}
\end{figure}
